CL-PFU: A suite of R packages for energy conversion chain analysis

### 2023-08-17 paper.Rmd
Reference for pins.

Max length: 250--1000 words. At the moment, we are at 1444 words.
But I saw many JOSS papers are longer than 1000 words. 
And our paper is describing many packages, whereas
most JOSS papers describe only a single package.
So I think we are going to be OK.
I think we can own the issue in the cover letter, 
saying that we are willing to consider splitting into
two papers upon the editor's advice.

@@

Both [targets][link-targets] pipelines 
(in the [PFUDatabase][link-pfudatabase] and
[PFUAggDatabase][link-pfuaggdatabase] packages)
benefit from the 
[PFUSetup][link-pfusetup] [@Heun-PFUSetup:2023] and
[PFUPipelineTools][link-pfupipelinetools] [@Heun-PFUPipelineTools:2023]
packages. 
[PFUSetup][link-pfusetup] identifies storage locations 
for pipeline input and output data.
[PFUPipelineTools][link-pfupipelinetools] provides functions and constants
common to both pipelines.

@@

```{r, eval=FALSE}
# (3) Run the PFUDatabase pipeline
targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))
# (4) Run the PFUAggDatabase pipeline
# targets::tar_make(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"), callr_function = NULL)
targets::tar_make_future(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"),
                         workers = 4)
```

@@

# Look at the aggregate PFU efficiency data frame
# created by the PFUAggDatabase pipeline
agg_eta_pfu <- pinboard |> 
  pins::pin_read("agg_eta_pfu", version = "")
head(agg_eta_pfu)
```

>>>>

<!-- Max length: 250--1000 words. At the moment, we are at 1444 words. -->
<!-- But I saw many JOSS papers are longer than 1000 words.  -->
<!-- And our paper is describing many packages, whereas -->
<!-- most JOSS papers describe only a single package. -->
<!-- So I think we are going to be OK. -->
<!-- I think we can own the issue in the cover letter,  -->
<!-- saying that we are willing to consider splitting into -->
<!-- two papers upon the editor's advice.  -->

@@

Both [targets][link-targets] pipelines 
(in the [PFUDatabase][link-pfudatabase] and
[PFUAggDatabase][link-pfuaggdatabase] packages)
produce data frames readable by the [pins][link-pins] package [@Silga:2023].
Both pipelines benefit from the 
[PFUSetup][link-pfusetup] [@Heun-PFUSetup:2023] and
[PFUPipelineTools][link-pfupipelinetools] [@Heun-PFUPipelineTools:2023]
packages. 
[PFUSetup][link-pfusetup] identifies storage locations 
for pipeline input and output data.
[PFUPipelineTools][link-pfupipelinetools] provides functions and constants
common to both pipelines.

@@

```{r, eval=FALSE}
# (3) Run the PFUDatabase pipeline
targets::tar_make(script = file.path("ExampleFolder", "_targets_pfudatabase.R"))
# (4) Run the PFUAggDatabase pipeline
targets::tar_make_future(script = file.path("ExampleFolder", "_targets_pfuaggdatabase.R"),
                         workers = 4)
```

@@

# Look at the aggregate PFU efficiency data frame
# created by the PFUAggDatabase pipeline
agg_eta_pfu <- pinboard |> 
  pins::pin_read("agg_eta_pfu", version = "20230817T180346Z-45741")
agg_eta_pfu |> 
  # Filter and delete columns 
  # to present a subset of exergy results in a data frame
  dplyr::filter(Energy.type == "X", IEAMW == "Both", 
                Product.aggregation == "Specified", 
                Industry.aggregation == "Specified", 
                GrossNet == "Net",
                Country %in% c("GHA", "ZAF")) |> 
  dplyr::mutate(
    Method = NULL, 
    Energy.type = NULL,
    Product.aggregation = NULL,
    Industry.aggregation = NULL,
    IEAMW = NULL,
    Chopped.mat = NULL, 
    Chopped.var = NULL, 
    GrossNet = NULL
  )
```
